\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-11 notes/2loopNLSM.tex
Corrected a power counting statment

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality (cite Zvi et al
paper).  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

The final essential constraint is unitarity.
Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only physical cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
This means that even at two loops, unitarity is still only probing the on-shell 4pt NLSM amplitude.
The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes in any scalar theory).
In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we enforce that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.

@@

The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
A generic term in the ZM numerator (of either basis graph) looks schematically like
\be
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8.
\ee
In other words, every term contains between 5 and 8 powers of loop momenta, as one would expect from a set of local, cubic Feynman rules.
\jm{I believe this is true but I need to check it.}
When the pion numerator is also forced to have this loop power counting, the number of generalized gauge freedom parameters reduces to 58.
The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}

>>>>

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

The final essential constraint is unitarity.
Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only physical cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
This means that even at two loops, unitarity is still only probing the on-shell 4pt NLSM amplitude.
The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we enforce that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.

@@

The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
A generic term in the ZM numerator (of either basis graph) looks schematically like
\be
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\ee
whereas a generic set of local, cubic Feynman rules could have produced terms with up to $m+n=12$ powers of loop momenta.
When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
